``Interestingness'' in Mathematical Theory Exploration

### 2019-04-26 PhDThesis/outline.tex
Thesis bits
Change bucketing to signature selection

\item Contributions:
  \begin{itemize}
  \item TEBenchmark (large, unambiguous empirical measurement and comparison)
  \item MLSpec (bucketing methods, recurrent clustering, etc.)
  \end{itemize}

@@

\item Bucketing (mostly paper and transfer report)
  \begin{itemize}
  \item Justification (exponential running times, large numbers of discarded
    equations, low precision, ...)
  \item Bucketing as a solution (big-O analysis, oracles, ...)
  \item Bucketing algorithms
    \begin{itemize}
    \item Pseudorandom features (baseline)
    \item Circular convolution (language agnostic, distributed representation,
      not learned)
    \item Recurrent clustering (Haskell-specific, not distributed, hand-crafted,
      solves global name problem)
    \item Non-recurrent clustering?
    \end{itemize}
  \item Application to TEBenchmark (impact on total recall)
  \item Discussion
    \begin{itemize}
    \item Pros and cons
    \end{itemize}
  \end{itemize}

@@

\item Conclusions
  \begin{itemize}
  \item Exploration is an important problem with many applications
  \item Hampered by ambiguous goals, small sample sizes, etc.
  \item Hampered by (lack of) efficiency
  \item Unambiguous benchmark is provided for comparison
  \item ``Smart'' bucketing method to improve efficiency
  \item Lots of room for future work (other corpora, other tools, other
    languages, applications of results, optimisation through profiling,
    abstraction invention through anti-unification, self-modelling, ...)
  \end{itemize}
\end{itemize}

>>>>

\item Contributions:
  \begin{itemize}
  \item TEBenchmark (large, unambiguous empirical measurement and comparison)
  \item MLSpec (signature selection methods, recurrent clustering, etc.)
  \end{itemize}

@@

\item Signature selection (mostly paper and transfer report)
  \begin{itemize}
  \item Justification (exponential running times, large numbers of discarded
    equations, low precision, ...)
  \item Signature selection as a solution (big-O analysis, oracles, ...)
  \item Signature selection algorithms
    \begin{itemize}
    \item Pseudorandom features (baseline)
    \item Circular convolution (language agnostic, distributed representation,
      not learned)
    \item Recurrent clustering (Haskell-specific, not distributed, hand-crafted,
      solves global name problem)
    \item Non-recurrent clustering?
    \end{itemize}
  \item Application to TEBenchmark (impact on total recall)
  \item Discussion
    \begin{itemize}
    \item Pros and cons
    \end{itemize}
  \end{itemize}

@@

\item Future Work

\item Conclusions
  \begin{itemize}
  \item Exploration is an important problem with many applications
  \item Hampered by ambiguous goals, small sample sizes, etc.
  \item Hampered by (lack of) efficiency
  \item Unambiguous benchmark is provided for comparison
  \item ``Smart'' signature selection method to improve efficiency
  \item Lots of room for future work (other corpora, other tools, other
    languages, applications of results, optimisation through profiling,
    abstraction invention through anti-unification, self-modelling, ...)
  \end{itemize}
\end{itemize}
